\Large\textsc{Regression And Resampling Techniques \\ FYS-STK4155 \\ Assignment One}

### 2019-09-17 assignment_one/article/main.tex
Working on article

\usepackage[]{mathtools}
\usepackage[]{amssymb}
\usepackage[]{libertine}
\usepackage[]{libertinust1math}
\usepackage[T1]{fontenc}
\usepackage[]{microtype}
\usepackage[]{geometry}
\usepackage[]{amsthm}
\usepackage[]{thmtools}
\usepackage[usedvipsnames]{xcolor}
\usepackage[]{bm}
\usepackage[]{amsmath}
\usepackage[]{commath}
\usepackage[]{todonotes}
\usepackage[]{graphicx}
\usepackage{titling}
\usepackage[]{FiraMono}
\usepackage[]{FiraSans}

@@

\title{\textsc{Regression And Resampling Techniques \\
  FYS-STK4155 \\
Assignment One}}
\author{Ivar Haugal{\o}kken Stangeby}

@@

\begin{document}
  \maketitle

@@

>>>>

\usepackage[]{mathtools}
\usepackage[]{amssymb}
\usepackage[]{libertine}
\usepackage[]{libertinust1math}
\usepackage[T1]{fontenc}
\usepackage[]{microtype}
\usepackage[]{geometry}
\usepackage[]{amsthm}
\usepackage[]{thmtools}
\usepackage[usedvipsnames]{xcolor}
\usepackage[]{bm}
\usepackage[]{amsmath}
\usepackage[]{commath}
\usepackage[]{todonotes}
\usepackage[]{graphicx}
\usepackage{titling}
\usepackage{mdframed}
\usepackage[]{FiraMono}
\usepackage[]{FiraSans}

@@

\title{\Large\textsc{Regression And Resampling Techniques \\
  FYS-STK4155 \\
Assignment One}}
\author{Ivar Haugal{\o}kken Stangeby}

@@

\begin{document}
  \maketitle 
  \clearpage

  \begin{abstract}
	  In this project, we implement and compare three different variants of
	  linear regression. Namely, ordinary least squares (OLS), Ridge
	  regression, and Lasso regression. We test the methods on terrain data
	  taken from a region near Stavanger, Norway. Initial implementation
	  tests are done on an artificial data-set based on noisy samples of
	  the Franke function. Statistical quantities pertaining to the various
	  model functions are computed and compared. We also give an
	  introduction to the theory and motivation behind the three methods.
  \end{abstract}

@@

  \chapter{Conclusion}

  \section{Further work}

  In this project we have discussed three different methods of linear
  regression.  In all three cases, we have fitted polynomial surfaces to the
  data sets. One draw-back with using polynomial surfaces is that they are
  inherently global methods. Thus, in order to capture local trends in the
  data, a very complex model is required, which (in the polynomial case) means
  surfaces of higher polynomial degree. In recent years, several attempts at
  constructing efficient local methods have been proposed. Spline-based
  (piecewise polynomial) methods in particular have been important, and several
  approaches to locally refined spline spaces have started to gain momentum.
  We note in particular that of \emph{hierarchical B-splines} (HB),
  \emph{truncated hierarchical B-splines} (THB) and \emph{locally refined
  B-splines} (LRB). These methods allow us to place more degrees of freedom in regions of high
  data-variance, thus locally increasing the model complexity.

  It would be interesting to make a comparison of the three methods in such a
  simple setting as linear regression, as done in this project, taking into
  account adaptive refinement of the spline spaces with respect to the sampled
  data set.
